Section rings of $\bq$-divisors on minimal rational surfaces

### 2017-12-18 surfaces-write-up/surface-paper.tex
consistent title spelling

\title[Section Rings of $\bq$-divisors]{Section Rings of $\bq$-divisors on minimal rational surfaces}

@@

After briefly stating our notation in Section~\ref{section:notation},
in Section~\ref{sec:proj}, we prove the following two results bounding
the degree of generators and relations of
section rings on $\bp^m$. The first applies
to effective $\bq$-divisors and the second applies to arbitrary
$\bq$-divisors.

>>>>

\title[Section rings of $\bq$-divisors]{Section rings of $\bq$-divisors on minimal rational surfaces}

@@

After briefly stating our notation in Section~\ref{section:notation},
in Section~\ref{sec:proj}, we prove the following two results bounding
the degree of generators and relations of
section rings on $\bp^m$. The first applies
to effective $\bq$-divisors and the second applies to arbitrary
$\bq$-divisors. Note that here we allow coefficients of divisors to be 0,
see Section~\ref{ssec:arbitrary-projective}.
